---
title: "Partnership for Safe Water Distribution Program - Disinfectant Residual Update"
output: html_document
date: "`r format(Sys.Date()-lubridate::days(30), '%B %Y')`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, include = FALSE, message = FALSE, warning = FALSE)
```

```{r}

#lims_dsn = "WinLIMS2"
#lims_uid = "lims_read"
#lims_pwd = "PWDLIMS01"
#owqm_dsn = "CWSDASHBOARD"
#owqm_uid = "cwsread"
#owqm_pwd = "cwsread"
#ops_dsn = "WaterOps"
#ops_uid = "wopsread"
#ops_pwd = "plant"


library(tidyverse)
library(wqr)
library(kableExtra)
library(rmarkdown)
library(knitr)
library(lubridate)
library(stringr)
library(blastula)
```

```{r}
sclass <- c("Routine Daily", "THMs/HAAs Monthly", "Violation Check Samples")
param <- c("Chlorine Residual Total", "Field-Chlorine Residual Total")
end_date <- floor_date(Sys.Date(), "month") #floor date rounds the current date down to the first of the month
start_date <- end_date - months(1)
dbp_start_date <- end_date - years(1) - months(1)
pm_start <- end_date - months(2)
year <- isoyear(start_date)
percentgrabsamples_start_date <- floor_date(Sys.Date(), "year") - years(7)
currentmonth <- (end_date - months(1))
pmonth <- currentmonth - months(1)
currentmonthlabel <- format(as.Date(currentmonth), '%B')
previousmonthlabel <- format(as.Date(pmonth), '%B')
```

```{r}
distribution_sites <- c(1101, 1102, 1103, 1104, 1106, 1107, 1201, 1300, 1301, 1302,
                        1303, 1304, 1305, 1401, 1601, 1602, 1603, 1604, 1608, 1701,
                        1702, 1704, 1705, 1707, 1708, 1710, 1711, 1712, 1713, 1715, 
                        1716, 1718, 1719, 1720, 1721, 2400, 2401, 2402, 2403, 2501,
                        2502, 2600, 2601, 2602, 2603, 2701, 2703, 2704, 2706,
                        2707, 2708, 2709, 2712, 2713, 2716, 2718, 3800, 3801, 3803, 
                        3804, 3901, 3904, 3905, 3906, 3907, 3909, 3911, 3912,
                        3913, 3914
                        ) #removed 2702, 3910. may have to include them to get accurate historical data?
distribution_sites <- c(distribution_sites, paste0(distribution_sites, c("U")), paste0(distribution_sites, c("D")))

rmvd_sites <- c(2702, 3910)
rmvd_sites <- c(rmvd_sites, paste0(rmvd_sites, c("U")), paste0(rmvd_sites, c("D")))

fieldstorsite <- c(7101, 7207, 7301, 7302, 7401, 7502, 7601)
fieldstorsite <- c(fieldstorsite, paste0(fieldstorsite, c("U")), paste0(fieldstorsite, c("D")))

labstorsite <- c(7102, 7103, 7200, 7201, 7300, 7303)
labstorsite <- c(labstorsite, paste0(labstorsite, c("U")), paste0(labstorsite, c("D")))

high_service_sites <- c(4001, 4005, 5004, 6001, 6002)
high_service_sites <- c(high_service_sites, paste0(high_service_sites, c("U")), paste0(high_service_sites, c("D")))

covid_sites <- c(1201, 1301, 2400, 2600, 3800)
covid_sites <- c(covid_sites, paste0(covid_sites, c("U")), paste0(covid_sites, c("D")))

allsites <- c(distribution_sites, fieldstorsite, labstorsite, high_service_sites, covid_sites, rmvd_sites)

```

```{r}
currentmonth <- read_LIMS(
  start_date = start_date,
  end_date = end_date,
  site = allsites,
  sample_class = sclass,
  parameter = c(param, "Coliforms Total (Colilert)")
) %>% filter(is.na(project_no) | project_no == "THM_HAA Monthly")
```

```{r}

countcurrent <- currentmonth %>% 
  pivot_wider(
    id_cols = c(lims_number, site, date_time),
    names_from = parameter,
    values_from = result
  ) %>% 
  rename(
    'field_chlorine'='Field-Chlorine Residual Total', 'lab_chlorine' = 'Chlorine Residual Total', 'total_coliforms' = 'Coliforms Total (Colilert)'
  ) %>% 
  filter(
    site %in% c(distribution_sites, fieldstorsite, covid_sites) & !is.na(field_chlorine)|
      site %in% c(labstorsite, high_service_sites) & !is.na(lab_chlorine)|
      site %in% c(distribution_sites, fieldstorsite, covid_sites) & is.na(field_chlorine) & !is.na(lab_chlorine)
  )%>% 
  mutate(
    type = ifelse(site %in% c(distribution_sites, fieldstorsite, covid_sites) & !is.na(field_chlorine) & !is.na(total_coliforms), "Field-Chlorine Residual Total/RTCR", 
                  ifelse(site %in% c(distribution_sites, fieldstorsite, covid_sites) & !is.na(field_chlorine) & is.na(total_coliforms), "Field-Chlorine Residual Total Only",
                  ifelse(site %in% c(labstorsite, high_service_sites) & !is.na(lab_chlorine), "Chlorine Residual Total",
                         ifelse(site %in% c(distribution_sites, fieldstorsite, covid_sites) & is.na(field_chlorine) & !is.na(lab_chlorine), "z", NA)))),
    
    result_to_use = ifelse(type == "z", lab_chlorine,
                           ifelse(type == "Field-Chlorine Residual Total/RTCR", field_chlorine,
                                  ifelse( type == "Chlorine Residual Total", lab_chlorine,
                                          ifelse( type == "Field-Chlorine Residual Total Only", field_chlorine, NA)))) 
  ) %>% 
  group_by(type
  ) %>% 
  summarise(count = n(),
            count_lessthan0.5 = sum(result_to_use<0.5),
            count_lessthan1 = sum(result_to_use<1)
  )

countcurrent <- countcurrent %>% 
  mutate(
    count_lessthan0.5 = ifelse(is.na(count_lessthan0.5), 0, count_lessthan0.5),
    count_lessthan1 = ifelse(is.na(count_lessthan1), 0, count_lessthan1),
    percent = (count_lessthan0.5/count)*100
  )

countcurrent<-countcurrent %>% 
  add_row(
    type = "Total", count = sum(countcurrent$count), count_lessthan0.5 = sum(countcurrent$count_lessthan0.5), count_lessthan1 = sum(countcurrent$count_lessthan1), percent = (sum(countcurrent$count_lessthan0.5)/sum(countcurrent$count))*100
  ) %>% 
  arrange(type) 
#PROBLEM WITH CURRENT SCRIPT IS THAT IT INCLUDES OCCT IN THE Z SAMPLES. FIGURE OUT HOW TO EXCLUDE THEM. Jan(1) and sep (4) - enddate
#have to arrange table this way to pick results out of it. Just in case there is a month where there is no instance of lab chlorine ONLY at a field site
#z represents field sites(distribution_sites, fieldstorsite, covid_sites) where no field data was taken but lab data was taken.
#typically these results are caused from DBP sites (2701 specifically) that are excluded when you query for field-chlorine individually (because there was only lab taken) but are included when you query for both parameters. 


coliformcount1 <- ifelse("Field-Chlorine Residual Total Only" %in% countcurrent$type, countcurrent$count[2], 0)
coliformcount2 <- ifelse("Field-Chlorine Residual Total Only" %in% countcurrent$type, countcurrent$count[3], 0)
drr_count <- ifelse("Field-Chlorine Residual Total Only" %in% countcurrent$type, countcurrent$count[3], countcurrent$count[2]) + coliformcount1
total_count <- ifelse("Field-Chlorine Residual Total Only" %in% countcurrent$type, countcurrent$count[4], countcurrent$count[3])

numless0.5 <- ifelse("Field-Chlorine Residual Total Only" %in% countcurrent$type, countcurrent$count_lessthan0.5[4], countcurrent$count_lessthan0.5[3])
numless1 <- ifelse("Field-Chlorine Residual Total Only" %in% countcurrent$type, countcurrent$count_lessthan1[4], countcurrent$count_lessthan1[3])
percentless0.5 <- ifelse("Field-Chlorine Residual Total Only" %in% countcurrent$type, countcurrent$percent[4], countcurrent$percent[3])

phrase <- ifelse("Field-Chlorine Residual Total Only" %in% countcurrent$type,paste(paste(drr_count, "field chlorine residual samples were collected in accordance with DRR requirements."), paste(coliformcount2, "field chlorine residual samples were collected in accordance with RTCR requirements.")), paste(drr_count, "field chlorine residual samples were collected in accordance with DRR/RTCR requirements."))

```

```{r}
num_site<-currentmonth %>% 
  group_by(site) %>% 
  summarise(
    count = n()
  )

site_count <- length(unique(num_site$site))
#count for num sites
```

```{r}
previousmonth <- read_LIMS(
  start_date = pm_start,
  end_date = start_date,
  site = allsites,
  sample_class = sclass,
  parameter = param
) %>% 
  filter(
    !is.na(result),
    is.na(project_no) | project_no == "THM_HAA Monthly"
  )
```

```{r}
countprevious <- previousmonth %>% 
  pivot_wider(
    id_cols = c(lims_number, site, date_time),
    names_from = parameter,
    values_from = result
  ) %>% 
  rename(
    'field_chlorine'='Field-Chlorine Residual Total', 'lab_chlorine' = 'Chlorine Residual Total'
    ) %>% 
  filter(
    site %in% c(distribution_sites, fieldstorsite, covid_sites) & !is.na(field_chlorine)|
      site %in% c(labstorsite, high_service_sites) & !is.na(lab_chlorine)|
      site %in% c(distribution_sites, fieldstorsite, covid_sites) & is.na(field_chlorine) & !is.na(lab_chlorine)
  ) %>% 
  mutate(
    type = ifelse(site %in% c(distribution_sites, fieldstorsite, covid_sites) & !is.na(field_chlorine), "Field-Chlorine Residual Total", 
                  ifelse(site %in% c(labstorsite, high_service_sites) & !is.na(lab_chlorine), "Chlorine Residual Total",
                  ifelse(site %in% c(distribution_sites, fieldstorsite, covid_sites) & is.na(field_chlorine) & !is.na(lab_chlorine), "z", NA))),
    result_to_use = ifelse(type == "zt", lab_chlorine,
                           ifelse(type == "Field-Chlorine Residual Total", field_chlorine,
                                  ifelse( type == "Chlorine Residual Total", lab_chlorine, NA))) 
     ) %>% 
  group_by(type
  ) %>% 
  summarise(count = n(),
            count_lessthan0.5 = sum(result_to_use<0.5),
            count_lessthan1 = sum(result_to_use<1)
            )
countprevious <- countprevious %>% 
  mutate(
    count_lessthan0.5 = ifelse(is.na(count_lessthan0.5), 0, count_lessthan0.5),
    count_lessthan1 = ifelse(is.na(count_lessthan1), 0, count_lessthan1),
    percent = (count_lessthan0.5/count)*100
  )

countprevious <- countprevious %>% 
  add_row(
    type = "Total", count = sum(countprevious$count), count_lessthan0.5 = sum(countprevious$count_lessthan0.5), count_lessthan1 = sum(countprevious$count_lessthan1), percent = (sum(countprevious$count_lessthan0.5)/sum(countprevious$count))*100
  ) %>% 
  arrange(type)
#have to arrange table this way to pick results out of it. Just in case there is a month where there is no instance of lab chlorine ONLY at a field site
#z stands for lab taken, not field at a field site

previous_rtcrdrr_count <- countprevious$count[2]
previous_total_count <- countprevious$count[3]
previous_numless0.5 <-  countprevious$count_lessthan0.5[3]
previous_numless1 <-  countprevious$count_lessthan1[3]
previous_percentless0.5 <-  countprevious$percent[3]

updown<- ifelse(total_count>previous_total_count, "up from", 
                ifelse(total_count<previous_total_count, "down from", 
                       "equal to"))

#counts for previous month
```

```{r}
dbp_df<- read_LIMS(
  site = c(distribution_sites, fieldstorsite, covid_sites),
  parameter = c("5 Haloacetic acids", "Total THMs"),
  sample_class = sclass,
  start_date = dbp_start_date,
  end_date = end_date
) %>% 
  filter(!is.na(result))
```

```{r}
tthm<- dbp_df %>%
  filter(
    parameter == "Total THMs"
  ) %>% 
  mutate(
    date_time = format(as.Date(date_time, format = "%Y-%m-%d"), "%Y-%m")
  ) %>% 
  group_by(date_time) %>% 
  summarise(tthm_min = min(result, na.rm = T),
            tthm_max = max(result, na.rm = T)) %>% 
  arrange(desc(date_time))

haa5<- dbp_df %>% 
  filter(
    parameter == "5 Haloacetic acids"
  ) %>% 
  mutate(
    date_time = format(as.Date(date_time, format = "%Y-%m-%d"), "%Y-%m")
  ) %>% 
  group_by(date_time) %>% 
  summarise(haa5_min = min(result, na.rm = T),
            haa5_max = max(result, na.rm = T)) %>% 
  arrange(desc(date_time))

dbp_table<-inner_join(
  tthm, 
  haa5,
  by = "date_time"
)

dbp_kable<- dbp_table %>% 
  mutate(across(matches("tthm_min|tthm_max|haa5_min|haa5_max"), ~round(.x, 1))) %>% 
  mutate(
    tthm_min = cell_spec(tthm_min, background = ifelse(tthm_min>80, "red", ifelse(tthm_min>60, "yellow", "white"))),
    tthm_max = cell_spec(tthm_max, background = ifelse(tthm_max>80, "red", ifelse(tthm_max>60, "yellow", "white"))),
    haa5_min = cell_spec(haa5_min, background = ifelse(haa5_min>60, "red", ifelse(haa5_min>45, "yellow", "white"))),
    haa5_max = cell_spec(haa5_max, background = ifelse(haa5_max>60, "red", ifelse(haa5_max>45, "yellow", "white")))
  ) %>% 
  kbl(caption = "Monthly Minimum and Maximum Total Trihalomethanes and 5 Haloacetic Acids", col.names = c("Date", "Total THM Minimum", "Total THM Maximum", "5 HAA Minimum (ug/L)", "5 HAA Maximum (ug/L"), escape = FALSE, align = rep('c', 5))%>%
  kable_classic(full_width = T) #kable table summarizing a years worth of DBP data
#kable table summarizing a years worth of DBP data
#dbp blurbs---------------------------------------------------------------------

tthm_blurb <- ifelse( 
  dbp_table$tthm_min[1]>dbp_table$tthm_min[2] && dbp_table$tthm_max[1]>dbp_table$tthm_max[2], 
  "Total THM values increased compared to last month.", 
  ifelse(
    dbp_table$tthm_min[1]>dbp_table$tthm_min[2] && dbp_table$tthm_max[1]<dbp_table$tthm_max[2],
    "Total THM Minimum increased and Total THM Maximum decreased compared to last month.",
    ifelse(
      dbp_table$tthm_min[1]<dbp_table$tthm_min[2] && dbp_table$tthm_max[1]>dbp_table$tthm_max[2],
      "Total THM Minimum decreased and Total THM Maximum increased compared to last month.",
      ifelse(
        dbp_table$tthm_min[1]<dbp_table$tthm_min[2] && dbp_table$tthm_max[1]<dbp_table$tthm_max[2],
        "Total THM values decreased compared to last month."
      )
    )
  ))

haa5_blurb <- ifelse( 
  dbp_table$haa5_min[1]>dbp_table$haa5_min[2] && dbp_table$haa5_max[1]>dbp_table$haa5_max[2], 
  "Total HAA5 values increased compared to last month.", 
  ifelse(
    dbp_table$haa5_min[1]>dbp_table$haa5_min[2] && dbp_table$haa5_max[1]<dbp_table$haa5_max[2],
    "Total HAA5 Minimum increased and Total HAA5 Maximum decreased compared to last month.",
    ifelse(
      dbp_table$haa5_min[1]<dbp_table$haa5_min[2] && dbp_table$haa5_max[1]>dbp_table$haa5_max[2],
      "Total HAA5 Minimum decreased and Total HAA5 Maximum increased compared to last month.",
      ifelse(
        dbp_table$haa5_min[1]<dbp_table$haa5_min[2] && dbp_table$haa5_max[1]<dbp_table$haa5_max[2],
        "Total HAA5 values decreased compared to last month."
      )
    )
  ))

#counts for number of dbp mcl exceedances in the month------------------------------

mcl_df<-read_LIMS(
  start_date = start_date,
  end_date = end_date,
  parameter = c("Total THMs", "5 Haloacetic acids"),
  sample_class = sclass,
  site = c(distribution_sites, covid_sites, fieldstorsite)
) #df used to get counts over the mcls. had to use a different date range then dbp_df

mcl<- mcl_df %>% 
  group_by(parameter) %>% 
  summarise(
    greater80 = sum(result>=80),
    greater60 = sum(result>=60)
  )
  
haa5exceed<-mcl$greater60[1]
tthmexceed<-mcl$greater80[2]

```

```{r}
column_dsc1 <- c(paste("Total DRR Samples for",paste(currentmonthlabel, year)), "# of samples < 1.00 mg/L", "# of samples >0.5 mg/L, <1.00 mg/L", "# of samples >0.15 mg/L, <0.50 mg/L", "# of samples <0.15 mg/L")
column_dsc2 <- c(" ","Below PWD distribution system goal of 1.00 mg/L", 
                 "Meets PfSW goal of 0.50 mg/L. Does not meet PWD distribution system goal 1.00 mg/L", 
                 "Meets PADEP minimum distribution residual required (0.15 mg/L). Does not meet: PfSW goal (0.50 mg/L), PWD distribution system goal (1.00 mg/L)", 
                 "Does not meet: PADEP minimum distribution residual required (0.15 mg/L), PfSW goal (0.50 mg/L), PWD distribution system goal (1.00 mg/L)")

summarytable <- read_LIMS(
  site = c(distribution_sites, covid_sites, fieldstorsite),
  start_date = start_date,
  end_date = end_date,
  sample_class = sclass,
  parameter = "Field-Chlorine Residual Total"
) %>%
  filter(
    is.na(result)==FALSE,
    is.na(project_no)==TRUE|project_no == "THM_HAA Monthly"
  )%>%
  group_by(month(date_time)) %>%
  summarise(count_lessthan1 = sum(result<1),
            countbetween1and0.5 = sum(result<1 & result>0.5),
            countbetween0.15and0.5 = sum(result<=0.5 & result>0.15),
            count_lessthan0.15 = sum(result<=0.15)) 
counts_vector <- c(drr_count, summarytable$count_lessthan1[1], summarytable$countbetween1and0.5[1], summarytable$countbetween0.15and0.5[1], summarytable$count_lessthan0.15[1])

summarytable <- data.frame(column_dsc1, counts_vector, column_dsc2 ) %>% 
  kbl(col.names = c("", "Count", "Description"), escape = FALSE, align = rep('c', 5))%>%
  column_spec(c(3), width = "20em") %>% 
  kable_classic(c("striped", "condensed")) 

```

```{r}
# add_dsop_monthly_counts(
#   year = year,
#   month = month(start_date),
#   n_total = total_count, #total_count
#   n_drr = drr_count, #drr_count
#   n_less_point5 = numless0.5, #numless0.5
#   n_less_one = numless1, #numless1
#   comments =NA
# )

monthly_table <- get_dsop_monthly_counts(
  start_year = year - 7,
  end_year = year) %>% 
  arrange(desc(year), desc(month)) %>%
  mutate(month = month(month, label=TRUE),
         p_less_point5 = round(p_less_point5, digits = 2)) %>% 
  rename(Year = "year") %>% 
  pivot_wider(
    id_cols = Year,
    names_from = month,
    values_from = p_less_point5
  )

monthly_kbl <-  monthly_table %>% mutate(
  Jan = as.numeric(Jan),
  Feb = as.numeric(Feb),
  Mar = as.numeric(Mar),
  Apr = as.numeric(Apr),
  May = as.numeric(May),
  Jun = as.numeric(Jun),
  Jul = as.numeric(Jul),
  Aug = as.numeric(Aug),
  Sep = as.numeric(Sep),
  Oct = as.numeric(Oct),
  Nov = as.numeric(Nov),
  Dec = as.numeric(Dec)
)

monthly_kbl <- monthly_kbl %>% pivot_longer(cols= c('Jul', 'Jun', 'May', 'Apr', 'Mar', 'Feb', 'Jan', 'Dec', 'Nov', 'Oct', 'Sep', 'Aug'),
                                            names_to = "month",
                                            values_to = 'percent')
monthly_kbl <- monthly_kbl %>% 
  mutate(
    percent = cell_spec(percent, background = ifelse(!is.na(percent) & percent >5.0, "red", ifelse(!is.na(percent) & percent > 4.0 & percent < 4.99, "orange", ifelse(!is.na(percent) & percent >3.0 & percent <3.99, "yellow", "white"))))
  )

monthly_kbl <- monthly_kbl %>% 
  pivot_wider(
    id_cols = "Year",
    names_from = "month",
    values_from = "percent"
  ) %>%
  select("Year", "Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec") %>% 
  kbl(caption = "Percent of Grab Samples < 0.50 mg/L TCL2 Residual - Entire PWD Distribution System - by Month", escape = FALSE, align = rep('c', 5))%>%
  kable_classic(full_width = T) #kable table summarizing a years worth of DBP data
```

Partnership for Safe Water Distribution Program -- Disinfectant Residual Update

The Bureau of Laboratory Services is responsible for administering compliance with the water quality monitoring requirements under both the federal Safe Drinking Water Act (SDWA) and state regulations. As monitoring locations that were temporarily not visited after the onset of COVID-19 are now being revisited, over 600 drinking water samples are collected from `r site_count` monitoring locations.

Regarding disinfectant residual, the Partnership for Safe Water has a numerical goal that 95% of monthly routine samples be within the following range:

**Total Chlorine Residual ≥ 0.50 mg/L and ≤ 4.0 mg/L**

PWD has met this goal for Partnership Years encompassing June 1, 2017 through May 31, 2021 (the Partnership year begins June 1st and runs through May 31st). From November 2017 -- July 2019, less than 1% of routine samples were below the Partnership goal of 0.50 mg/L for every month. The last month that PWD did not meet the 95% Partnership goal was September 2016 (7.27% of monthly samples were below 0.50 mg/L), with the following two Septembers having less than 2% of samples below 0.50 mg/L and meeting Partnership's monthly goal. The highest percentage of monthly Partnership samples not meeting the goal in the previous three calendar years (2019 -- 2021) was 2.78% in September 2020.

A total of `r total_count` samples were collected in `r currentmonthlabel` `r year`, `r updown` `r previous_total_count` samples collected in `r previousmonthlabel`. `r phrase` PWD adjusted the sampling schedule and frequency starting in the second half of March 2020 due to the ongoing COVID-19 pandemic. PWD is still collecting more than the required 360 samples for RTCR/DRR compliance. Starting in November 2020, PWD began to resume sampling from some routine fire and police stations for the RTCR/DRR compliance program. The selected fire and police stations are the locations that are sampled monthly as part of the DBP monitoring program as well. PWD also began resuming sample collection samples from additional fire and police stations earlier this year that were not being sampled during the first year of the pandemic. Starting in July 2020, PWD resumed monthly distribution Disinfection By-Product sampling from the normal fire and police station locations. As of October 2021, Chestnut Hill Hospital is no longer be sampled from and the Chestnut Hill Pressure District Pump Station replaced the hospital as the routine sampling location for the Chestnut Hill pressure district.

<u>*`r currentmonthlabel` `r year` had `r numless0.5` samples below 0.50 mg/l throughout the distribution system, and `r numless1` samples below 1 mg/l.*</u>

```{r include = TRUE, echo = FALSE}
summarytable
```

`r tthm_blurb` `r tthmexceed` locations had single sample TTHM results above the MCL of 80 ppb. Single sample TTHM results above the MCL are not an MCL exceedance as compliance with the MCL is based on Locational Running Averages.

`r haa5_blurb` `r haa5exceed` locations had single sample HAA5 results above the MCL of 60 ppb. Single sample HAA5 results above the MCL are not an MCL exceedance as compliance with the MCL is based on Locational Running Averages.

Below is a monthly range of DBP distribution values for the last 13 months. Values that exceed the MCL for a single sample are highlighted in red, and samples that exceed the operational goal of 75% of the MCL are in yellow.

```{r include = TRUE, echo=FALSE}
dbp_kable
```

TTHM LRAA MCL = `r text_spec("80 µg/L", color = "white", background = "red")`; Operational Goal = `r text_spec("60 µg/L", color = "black", background = "yellow")`

HAA5 LRAA MCL = `r text_spec("60 µg/L", color = "white", background = "red")`; Operational Goal = `r text_spec("45 µg/L", color = "black", background = "yellow")`

```{r include = T, echo = F}
monthly_kbl
```

Key

`r text_spec(">5.0 % * Fails Partnership Goal", color = "black", background = "red")`

`r text_spec("4.0-4.99 %", color = "black", background = "orange")`

`r text_spec("3.0-3.99 %", color = "black", background = "yellow")`

`r text_spec("0-2.99 %", color = "black", background = "white")`

```{r}
render_connect_email("PFSW Report Email.Rmd") %>% 
  attach_connect_email(subject = "PFSW Report", attach_output = TRUE)

```
